\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-06 report/article_4.tex
report update

When considering a property in a given area, you may ask a realtor
questions like: how do prices here compare to surrounding postcodes?
How have prices increased over time?  A real estate professional can
give an opinion based on their own limited sample size, but with a
large dataset we can address these questions quantitatively and
visualise the results.

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
\begin{center}
\includegraphics[width=.44\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

@@

Given a time series of housing prices, it's of interest to investors
to speculate on potential investment returns for a given property
area. This can be done through time series analysis using the
autoregressive integrated moving average (ARIMA) model (Figure
2). Investment returns can be optimised by selecting areas with
maximal growth projections.\textsuperscript{$\star$} \\

@@

\vspace{-2em}
\subsection*{Investment grading}

@@

As an example, Figure 3 shows the top 5 best-ranked postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. \\

@@

The rankings used in Figure 3 made use of the $drift$ parameter of
ARIMA models, combined with statistical volatility over the five year
house prices dataset. Both parameters were converted to quantiles and
weighted equally, with those sectors with the largest projected growth
and lowest historical volatility receive the highest investment grade.

\vspace{-1em}
\section*{Summary}
These initial

@@

\logo \hspace{.1em} would first be released as both a web service and
associated apps for mobiles and tablets. These would offer limited
analysis and visualisation for free, with user analytics and feedback
helping to validate the business model.

@@

>>>>

When considering a property in a given area, you may ask a realtor
questions like: how do prices here compare to surrounding postcodes?
How have prices increased over time? And how have prices changed over
time? A real estate professional can give an opinion based on their
own limited sample size, but with a large dataset we can address these
questions quantitatively and visualise the results.

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.5\textwidth}
\vspace{1em}
\begin{center}
\includegraphics[width=.48\textwidth]{Figures/fractal.png}
\vspace{.5em}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

@@

Given a time series of housing prices, it's of interest to investors
to speculate on potential investment returns for a given property
area. This can be done through time series analysis using the
autoregressive integrated moving average (ARIMA) model (Figure 2). The
model fitting procedure included regularisation that allowed a $drift$
term to model non-stationary trends, as well as coefficients capturing
periodicity or seasonal effects. Potential investment returns could be
optimised by selecting areas with
maximal growth projections. \\

@@

\vspace{-1em}
\subsection*{Investment grading}

@@

As an example, Figure 3 shows the top 5 best-ranked postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. These include South London
suburbs of Upper Tooting and Morden, Walthamstow, as well as Brockley,
whose train station within SE4 1 was linked with the London overground network in 2010.\\

@@

The rankings used in Figure 3 made use of the $drift$ parameter of
ARIMA models, combined with statistical volatility over the five year
house prices dataset. Both parameters were converted to quantiles and
weighted equally, with those sectors with the largest projected growth
and lowest historical volatility receive the highest investment grade.\textsuperscript{$\star$}

@@

\subsection*{Socio-economic value}

\subsection*{Initial product}
\logo \hspace{.1em} would first be released as both a web service and
associated apps for mobiles and tablets. These would offer limited
analysis and visualisation for free, with user analytics and feedback
helping to validate the business model.

@@

\subsection*{Business development}
